\cvsection{Experience}

\begin{cventries}
  \cventry
    {Software Engineer} % Job title
    {Navico Group} % Organization
    {Auckland, New Zealand} % Location
    {Nov. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and deployed several \textbf{full-stack} web apps single-handedly from scratch.}
        \item {Set up web servers and \textbf{network infrastructure} for the R\&D department.}
        \item {Updated and extended a large-scale \textbf{Python} automated testing platform.}
        \item {Implemented \textbf{CI/CD} pipelines and \textbf{dockerized} projects.}
      \end{cvitems}
    }

    \cventry
    {Software Engineering Intern} % Job title
    {Koda Web} % Organization
    {Auckland, New Zealand} % Location
    {Feb. 2022 - June 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Updated and patched legacy \textbf{Visual Basic} codebase.
        \item Implemented \textbf{backend} endpoints for clients relating to the transfer of data from hardware via serial port.
        \item Developed \textbf{UI/UX} drawings and implemented them using \textbf{React}.
      \end{cvitems}
    }

  \cventry
    {Software Engineering Intern} % Job title
    {Navico Group} % Organization
    {Auckland, New Zealand} % Location
    {Nov. 2021 - Feb. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Implemented a \textbf{Unity} simulation related to testing prototype hardware.
        \item Collaborated as a team to implement a large-scale \textbf{Python} project that pooled together data simulators using a GUI.
      \end{cvitems}
    }

\end{cventries}
